survNRI
============================

This package contains a single function `survNRI` which calculates the NRI for survival data using up to five different estimators. The different methods available are:

- *KM* = Kaplan- Meier estimator 
- *IPW* = Inverse probability weighted estimator 
- *SmoothIPW* = Smooth inverse probability weighted estimator 
- *SEM* = Semi-parametric estimator
- *Combined*= Combined estimator as described (along with all other estimates) in the reference paper.

### Tutorial


```{r}
library(survNRI)
#some simulated data for example. 
data(SimData)

#take a look 
head(SimData)
```

Calculate the NRI using all estimators at future time 2.


```{r}
#bootstrap only 10 times to reduce computation for this example. 
survNRI( time  = "stime", event = "status", model1 = "y1", model2 = c("y1", "y2"), data = SimData, 
         predict.time = 2, method = "all", bootMethod = "normal",  bootstraps = 10, alpha = .05)
```

Now only estimate using the smooth IPW, SEM and combined methods. 

```{r}
tmp <- survNRI( time  = "stime", event = "status", model1 = "y1", model2 = c("y1", "y2"), data = SimData, 
         predict.time = 3, method = c("SmoothIPW", "SEM", "Combined"), bootMethod = "percentile", bootstraps = 10, alpha = .01)

#look at the results
tmp
```

```{r}
#access estimates and ci's
tmp$estimates
tmp$CI
```


for more information see `?survNRI`. 

### References 

*Lifetime Data Analysis* 2012 Dec 20. [Epub ahead of print] Evaluating incremental values from new predictors with net reclassification improvement in survival analysis. Zheng Y, Parast L, Cai T, Brown M. PMID: 23254468



